Exoplanet population inferences from a hierarchical model of the \Kepler\ ``Object of Interest'' Catalog

### 2013-11-21 document/ms.tex
title, abstract, and two (2)

\title{%
    Probabilistic hierarchical modeling of exoplanet populations using
    incomplete catalogs
}

@@

\begin{abstract}

\end{abstract}

\keywords{%
}

@@

We start by assuming that ever target star has some $K$ orbiting planets.
Most of these planets are unobserved because they are two small to be
detectable or because of geometry.
The graphical model in \fig{gm} is a sketch of the hypothetical generative
procedure for a catalog of exoplanet observations.
The way it is shown, this model is extremely general but we will consider a
very specific form here.
The parameters of this model are listed and described in \tab{parameters}.

>>>>

\title{%
    Exoplanet population inferences
    from a hierarchical model
    of the \Kepler\ ``Object of Interest'' Catalog
}

@@

\begin{abstract}
The catalog of \Kepler\ Objects of Interest (KOI) is a list of putative periodic exoplanet transit signals
  discovered in the photometric data from the \Kepler Satellite.
In principle this catalog contains a wealth of statistical information about the full population of exoplanets.
Here we construct a model of the population that explains the content of the catalog.
Our approach is novel in that
  it takes the form of a rigorous (if approximate) hierarchical Bayesian inference,
  it includes a parameterization of a non-trivial selection function (incompleteness),
  and we fully marginalize out all latent and nuisance parameters using sampling.
Because the model is properly hierarchical,
  it can be constrained by multiple data sources;
  we demonstrate this by adding the Solar System as a constraint,
  but extensions to radial velocity, direct detection, and astrometric surveys would also be straightforward.
Approximations abound:
  Simple parameterized forms are assumed for the multivariate distribution of exoplanet parameters,
  incompleteness is assumed to depend only on a scalar related to signal-to-noise,
  and the KOI catalog is assumed to be dominated by real (not false-positive) exoplanet signals.
We find XXX and YYY.
\end{abstract}

\keywords{%
methods:statistical
}

@@

We start by assuming that ever target star has some $K$ orbiting planets.
Most of these planets are unobserved because they are two (2) small to be
detectable or because of geometry.
The graphical model in \fig{gm} is a sketch of the hypothetical generative
procedure for a catalog of exoplanet observations.
The way it is shown, this model is extremely general but we will consider a
very specific form here.
The parameters of this model are listed and described in \tab{parameters}.
